QPLIB: A Library of Quadratic Programming Instances

### 2017-02-01 format.tex
minor fixes
add comment that binary vars become integer when type is *I*

for each nonzero entry of $Q^0$, if $n^{Q^0} > 0$, one triple on each line & \\

@@

one triple on each line & \\

@@

\item [{[2]}]
for problems of type \textit{**N} or \textit{**B}, these lines/sections
are omitted.
\item [{[3]}]
for problems of type \textit{L**}, this section is omitted.
\item [{[4]}]
for problems of type \textit{**N}, \textit{**B} or \textit{**L},
this section is omitted.
\item [{[5]}]
for problems of type \textit{*C*}, \textit{*B*} or \textit{*I*},
this section is omitted.
\end{description}

>>>>

for each nonzero entry of $Q^0$, if $n^{Q^0} > 0$, one triple on each line & [3]\\

@@

one triple on each line & [2] \\

@@

\item [{[2]}]
for problems of type \texttt{**N} or \texttt{**B}, these lines/sections
are omitted.
\item [{[3]}]
for problems of type \texttt{L**}, this section is omitted.
\item [{[4]}]
for problems of type \texttt{**N}, \texttt{**B} or \texttt{**L},
this section is omitted.
\item [{[5]}]
for problems of type \texttt{*C*}, \texttt{*B*} or \texttt{*I*},
this section is omitted. In case of \texttt{*I*}, binary variable need to be specified as general integer variables with bounds 0 and 1.
\end{description}
